\documentclass[a4paper,12pt]{article}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[margin=0.2in]{geometry}

\usepackage{enumitem}
\usepackage{titling}
\usepackage{xcolor}
\pagenumbering{gobble}

\newcommand{\sectionline}{\vspace{0.2pt}\noindent\rule{\linewidth}{0.4pt}\vspace{2pt}}

\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=10pt}
\titleformat{\section}{\bfseries\large}{}{0em}{}
\titlespacing*{\section}{0pt}{0.4pt}{0.2pt}

\begin{document}

% ----- Header -----
% ----- Header -----
\begin{center}
    {\LARGE \textbf{Srinivas}} \\[4pt]
    \href{mailto:srinupullela2004@gmail.com}{srinupullela2004@gmail.com} \quad | \quad 
    +91- 6363039960\quad | \quad 
    \href{https://linkedin.com/in/srinivas---p}{linkedin.com/in/srinivas---p} \quad | \quad 
    \href{https://github.com/srinivas-pullela}{github.com/srinivas-pullela} \quad | \quad 
    Sindhanur, Karnataka, India
\end{center}
\sectionline

% ----- Career Objective -----
\section*{Career Objective}
Motivated and detail-oriented \textbf{Data Science fresher} with a strong foundation in statistics, programming, and machine learning. Passionate about analyzing data, building predictive models, and applying AI-driven techniques to solve real-world business challenges. Seeking an entry-level role as a \textbf{Data Scientist} to contribute to data-driven decision-making.\\
\sectionline

% ----- Technical Skills -----
\section*{Technical Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} Python
    \item \textbf{Data Analysis \& ML Libraries:} NumPy, Pandas, Scikit-learn, TensorFlow, Matplotlib, Seaborn
    \item \textbf{Data Visualization Tools:} Power BI, Matplotlib
    \item \textbf{Databases:} MySQL, Oracle SQL
    \item \textbf{Tools \& IDEs:} Jupyter Notebook, Anaconda, VS Code, Git, Excel
\end{itemize}
\sectionline

% ----- Academic Projects -----
\section*{Academic Projects\\}

\textbf{1. Predict Fare of Airline Tickets using Machine Learning} \textit{--Python, Pandas, Scikit-learn, Matplotlib}\\[-5pt]
\begin{itemize}
    \item Collected and preprocessed airline ticket datasets to analyze pricing patterns.
    \item Applied regression models to predict ticket prices based on time, airline, and route.
    \item Achieved reliable predictions by optimizing hyperparameters.\\
\end{itemize}

\textbf{2. Building and Deploying a Movie Recommendation System} \textit{--Python, Streamlit, Scikit-learn}\\[-5pt]
\begin{itemize}
    \item Developed a content-based recommendation engine using cosine similarity.
    \item Integrated TMDb API to fetch movie posters dynamically.
    \item Deployed the model using Streamlit for easy web access.\\
\end{itemize}

\textbf{3. Predict Stock Prices using Time Series Analysis} \textit{--Python, Pandas, ARIMA, LSTM}\\[-5pt]
\begin{itemize}
    \item Collected historical stock data using Yahoo Finance API.
    \item Applied ARIMA and LSTM models for future stock price prediction.
    \item Visualized trends and evaluated performance using RMSE and MAE metrics.
\end{itemize}
\sectionline

% ----- Education -----
\section*{Education}
\textbf{Bachelor of Engineering (B.E.) – Computer Science and Engineering} \\
Government Engineering College, Raichur (GECR) \hfill \textit{2022 – 2026}\\
\textbf{CGPA:} 8.2 / 10 (Expected)\\
\sectionline

% ----- Certifications -----
\section*{Certifications}
\begin{itemize}
    \item Data Science Internship – CodeAlpha (2025 - Ongoing) 
    \item Python for Data Science – Infosys Springboard (Ongoing)
    \item AI Foundations -- Oracle certified
    \item Data Science – Oracle certified
\end{itemize}
\sectionline

% ----- Soft Skills -----
\section*{Soft Skills}
Problem Solving \quad | \quad Communication \quad | \quad Teamwork \quad | \quad Adaptability \quad | \quad Time Management\\
\sectionline

% ----- Languages -----
\section*{Languages Known}
English \quad | \quad Kannada \quad | \quad Telugu \quad | \quad Hindi

\end{document}
